Verifying Demonstrations

### 2019-09-12 paper/DB-anon-cred.tex
Writes up DBSHW to solve DF resistance

\subsection{Achieving \acs*{DBDF} resistance}

@@

The \ac{DB} phase protects against distance fraud.
Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).

>>>>

\subsection{\Iacs*{DBDF} resistant protocol}

@@

We will now introduce an extended protocol, \(\DBSHW\), which represents the 
secure hardware implementation.
\Cref{DBSHW-overview} presents an overview.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\HWprove[g, q, \alpha]\):
    & &
    \(\HWverify[g, q, A]\):
    \\
    \midrule

    Static \(\sk_P, \cert_P\colon \pk_P = \hat g^{\sk_P}\)
    &
    & \(\sk_V, \pk_V = \hat g^{\sk_V}\)\\

    \midrule
    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\

    \(\cert_P\)
    & \(\ProtoSendRight{\cert_P}\)
    & \(k \gets \pk_P^{\sk_V}\)
    \\

    \(k \gets \pk_V^{\sk_P}\)
    & \(\ProtoSendLeft{\pk_V}\)
    & \(\pk_V\)
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Setup}} \\

    Load \(k\) into \(\UWBPR\)
    &
    & Load \(k\) into \(\UWBPR\)
    \\

    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho} g^{\hat\rho}\)
    & \(\ProtoSendRight{R}\)
    & \(\hat A\gets A \pk_P\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
    \\

    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
    &
    &
    \\

    \(s_m\gets \rho - c_m\alpha \pmod q\)
    &
    &
    \\

    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
    &
    &
    \\

    % null
    & \(\ProtoSendLeft{i}\)
    & \(i\rgets \{1, \dotsc, m\}\), start clock
    \\

    Fetch \(s_i, \hat s_i\)
    & \(\ProtoSendRight{s_i, \hat s_i}\)
    & Stop clock, record \(\Delta t\)
    \\

    % null
    &
    & Accept if \(R =  \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and \(\Delta t 
      < t_{\max}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

The \(\DBSHW\) secure hardware device must contain a (static) private 
key~\(\sk_P\) (for the prover, \(\sk_V\) for the verifier) with a digital 
certificate~\(\cert_P\) (and \(\cert_V\)) for the public key~\(\pk_P\) (and 
\(\pk_V\)).

\paragraph*{Pre-setup}

The pre-setup phase consists of an authenticated key agreement.
We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
agreement protocol based on discrete logarithms can be used.
The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
If the prover's certificate is invalid, the protocol aborts.

\paragraph*{Setup}

The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
\(\PK[\alpha, \sk_P][\hat A = g^\alpha \hat g^{\sk_P}]\).
\daniel{Or is it better to do \(\PK[\alpha, \sk_P][A = g^\alpha \land \hat A = 
    \hat g^{\sk_P}]\)?}
They use the agreed upon key~\(k\) as the key for \(\UWBPR\).

The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets g^\rho 
  \hat g^{\hat\rho}\).
The verifier computes \(\hat A\gets A \pk_P\), where \(A\) is the value for 
which the prover must prove knowledge of the discrete logarithm.

The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).

\paragraph*{Distance bounding}

The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
\(\UWBPR\) reply.
The verifier stops the clock and records the round-trip time~\(\delta t\).

\paragraph*{Verification}

The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
the round-trip time \(\delta t < t_{\max}\) does not exceed the 
limit~\(t_{\max}\).

\subsection{\acs*{DBDF} resistance}

This protocol uses the \ac{DBMF} resistance of \(\DBS\) to ensure \ac{DBDF} 
resistance against a malicious prover.
The trusted hardware uses the authenticated key agreement to establish the 
shared secret \(k\), thus a verifier prevents a malicious prover from learning 
\(k\) --- the main limit of~\cite{UWBPR}.
